Reasoning About a Machine with Local Capabilities

### 2018-05-14 toplas/paper.tex
Disabled comments and colouring
Updated the new TOPLAS introduction

\definecolor{OliveGreen}{RGB}{60,128,49}
\definecolor{Blue}{RGB}{92,26,143}
\newenvironment{toplas}
    {\color{OliveGreen}}{}
\newenvironment{toplassug}
    {\color{Blue}}{}

\newcommand{\itoplas}[1]
    {{\color{OliveGreen} #1}}
\newcommand{\itoplassug}[1]
    {{\color{Blue} #1}}

@@

\begin{toplas}
  This paper is an extension of a published conference
  paper\citep[Skorstengaard:esop2018]. We have made minor improvements to
  readability and completeness throughout the paper, but we highlight the
  following changes:
  \begin{itemize}
  \item We have added an introduction to the \sectionname~\nameref{sec:logical-relation} that provide informal intuition about how the logical relation machinery comes into play in this setting.
  \item We have added a proof sketch for the \nameref{thm:ftlr} and one for Lemma~\ref{lem:correctness-g1}, the correctness lemma for the awkward example.
  \item We have added figures that illustrate central parts of the calling convention.
  \item We have added a section on malloc.
    In particular, we provide the specification for malloc used in the examples of the paper.
  \item We have added a section on macro instructions.
    All the macro instructions are described and the implementation of \texttt{scall} is provided.
  \item We have added a section on reasoning about programs that run on a capability machine.
  \item We have added many details previously found only in the technical appendix~\citep{technical_appendix} to the paper.
    Many of the details we did not include in the paper are now in the appendix of the paper.
  \end{itemize}
\end{toplas}

>>>>

\definecolor{OliveGreen}{RGB}{60,128,49}
\definecolor{Blue}{RGB}{92,26,143}
\newenvironment{toplas}{}{}
%    {\color{OliveGreen}}{}
\newenvironment{toplassug}
    {\begin{comment}}{\end{comment}}

\newcommand{\itoplas}[1]{#1}
%    {{\color{OliveGreen} #1}}
\newcommand{\itoplassug}[1]{}
%    {{\color{Blue} #1}}

@@

\begin{toplas}
  This paper is an extension of a published conference paper\citep{Skorstengaard:esop18}.
  We have made minor improvements to readability and completeness throughout the paper, but we highlight the following changes:
  \begin{itemize}
  \item We have added an introduction to the \sectionname~\nameref{sec:logical-relation} that provide informal intuition about how the logical relation machinery comes into play on a capability machine.
  \item We have added a proof sketches for the \nameref{thm:ftlr} and Lemma~\ref{lem:correctness-g1}, the correctness lemma for the awkward example.
  \item We have added figures that illustrate central parts of the calling convention.
  \item We have added a section on malloc.
    Specifically, we provide the specification for the malloc used in the examples of the paper.
  \item We have added a section on macro instructions with descriptions of all the macros and the implementation of \texttt{scall}.
  \item We have added a section on reasoning about programs that run on a capability machine.
    This section explains how one reason about common scenarios that arise in programs on a capability machine, and in particular how the logical relation is used.
    It also introduces a number of lemmas that prove recurring bits once and for all.
  \item We have added many details previously found only in the technical appendix~\citep{technical_appendix} to the paper.
    Further, many of the details we did still not include in the paper are now in the appendix of this paper.
  \end{itemize}
\end{toplas}
